News Image Captioning with Transformers

### 2019-10-12 paper/paper.tex
Update contributions

\begin{itemize}
   \item We scraped articles and images from the New York Times to create the
   largest news image captioning with 794K images, each with an associated
   caption and article.
   \item We use the transformer architecture and Byte Pair Encoding to develop
   an end-to-end encoder-decoder model that achieves state-of-the-art results
   on news image captioning.
   \item
\end{itemize}

>>>>

\begin{itemize}
   \item We show that combining article attention with pre-trained contextualized
   word piece embeddings allows our model to generate captions containing
   relevant words that were not seen during training.

   \item We demonstrate that the location of the image within the article is an
   important signal for generating relevant news captions.

   \item We build on the “Good News” dataset to produce a larger and more complete
   news captioning dataset consisting of * articles from the New York Times and
   their 794K images with captions. In contrast to “Good News” our dataset
   contains the full article text, and the location of the image within the
   page.
\end{itemize}
